Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2022-02-18 paper/SupMat.Rnw

%***DAN: Jasmin, please start on this section when you get a chance. Here are some topics that need
%to be covered:
Estimations of $Q_i(t)$, $V_i(t)$, and $K_i(t)$, temperature dependence functions for 
cell quota, reproduction rate, and half saturation, respectively, were used to 
paramaterize the competing diatom model outlined in the paper. 
Values of and subsequent function estimations are plotted in Figure \ref{fig:VQK}. 
\cite{Descamps_2005} obtained estimated values for $Q_i$, $V_i$, and $K_i$ from 
single species nine-day batch experiments at four different temperatures ($6^\circ$C, 
$12^\circ$C, $18^\circ$C, $24^\circ$C) (see Table 1 of \cite{Descamps_2005}) and further
computed linear interpolations to
functions $Q_i(t)$, $V_i(t)$, and $K_i(t)$. These values and functions are 
indicated in Figure \ref{fig:VKQ} by open circles and dashed lines. 
\cite{Ellne_2016, Ellner_2019} used slightly modified values and functions,
indicated in \ref{fig:VQK} by filled circles and solid lines. 
Our investigation follows that of \cite{Ellne_2016, Ellner_2019} and 
uses the modified functions of  $Q_i(t)$, $V_i(t)$, and $K_i(t)$ to analyze coexistence.

@@

@@

\begin{figure}
\includegraphics[width=.66\textwidth]{../results_figs/VKQfig.pdf}
\caption[Species growth rate, silica uptake, and half sturation responses to changes in temperature.]
{Species maximum growth rate (a), half saturation constant (b), and silica uptake (c) responses to changes in temperature. Species 1 is \emph{F. crotonensis}, shown in blue, and species 2 is \emph{C. pseudostelligera}, shown in red. Open circles and dashed lines indicate estimated data and interpolations from \cite{Gonzalez_2005} and closed circles and solid lines indicate values and function used in our analysis as defined in \cite{Ellner_2016, Ellner_2019}. \label{fig:VKQ}}
\end{figure}

>>>>

%***DAN: Jasmin, please start on this section when you get a chance. Here are some topics that need
%to be covered:
Estimations of $Q_i(t)$, $V_i(t)$, and $K_i(t)$, temperature dependence functions for 
cell quota, reproduction rate, and half saturation, respectively, were used to 
paramaterize the competing diatom model outlined in the paper. 
Values of and subsequent function estimations are plotted in Figure \ref{fig:VQK}. 
\cite{Descamps_2005} obtained estimated values for $Q_i$, $V_i$, and $K_i$ from 
single species nine-day batch experiments at four different temperatures ($6^\circ$C, 
$12^\circ$C, $18^\circ$C, $24^\circ$C) (see Table 1 of \cite{Descamps_2005}) and further
computed linear interpolations to
functions $Q_i(t)$, $V_i(t)$, and $K_i(t)$. These values and functions are 
indicated in Figure \ref{fig:VKQ} by open circles and dashed lines. 
\cite{Ellner_2016, Ellner_2019} used slightly modified values and functions,
indicated in \ref{fig:VQK} by filled circles and solid lines. 
Our investigation follows that of \cite{Ellner_2016, Ellner_2019} and 
uses the modified functions of  $Q_i(t)$, $V_i(t)$, and $K_i(t)$ to analyze coexistence.

@@

\section{\emph{Cyclotella psedosteligera} as the invader}\label{sect:Invader2}
We generated plots analougous to Fig. \ref{MT-fig:fig5} and Fig. \ref{MT-fig:fig6} for the reverse invader-resident scenario where \emph{C. pseudosteligera} is the invader and \emph{F. crotonensis} is the resisent to compute the IGR and decompose coexistence mechanisms of \emph{C. pseudosteligera}. Fig. \ref{fig:fig5_2} is analogous to Fig. \ref{MT-fig:fig5} and shows changes in the IGR and decomposed mechanisms in response to change in one temperature parameter while the other two are held constant. Within the parameters of our simulations, the IGR of \emph{C. pseudosteligera}

@@

\begin{figure}
\includegraphics[width=.66\textwidth]{../results_figs/VKQfig.pdf}
\caption[Species growth rate, silica uptake, and half sturation responses to changes in temperature.]
{Species maximum growth rate (a), half saturation constant (b), and silica uptake (c) responses to changes in temperature. Species 1 is \emph{F. crotonensis}, shown in blue, and species 2 is \emph{C. pseudostelligera}, shown in red. Open circles and dashed lines indicate estimated data and interpolations from \cite{Descamps_2005} and closed circles and solid lines indicate values and function used in our analysis as defined in \cite{Ellner_2016, Ellner_2019}. \label{fig:VKQ}}
\end{figure}
